The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-02-27 RET_Hosts.tex
Updates from Overleaf

\toprule
{} &       RA &       Dec &    $m_r$\tnote{a}  &     $z$ &     Survey & Exposure time (hours) \tnote{b} \\
Transient name &          &           &          &         &         &            &               \\
\midrule
DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.6479 &      OzDES &       6.58 \\
DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.1964 &      OzDES &      10.16 \\
DES13S2wxf     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.5698 &      OzDES &       5.41 \\
DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.5823 &      OzDES &       4.00 \\
DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.7120 &      OzDES &      45.50 \\
DES13X3gmd     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.7808 &      OzDES &      13.91 \\
DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.3457 &  NOAO\_0522 &               \\
DES13C3uig     & 52.94416 & -27.58544 & $22.17 \pm 0.03$ & 0.6734 &       ACES &               \\
DES13X2wvv     & 34.86526 &  -6.71603 & $21.89 \pm 0.02$ & 0.4750 &      OzDES &       4.50 \\
DES14S2anq     & 41.27776 &  -0.74529 & $17.57 \pm 0.03$ & 0.0521 &      OzDES &       0.75 \\
DES14X1bnh     & 33.74902 &  -4.79254 & $21.95 \pm 0.03$ & 0.8298 &      OzDES &       3.50 \\
DES15S1fli     & 43.18790 &  -0.88620 & $20.98 \pm 0.02$ & 0.4473 &      OzDES &       2.33 \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citet{Wiseman2020}.
\item[b] Exposure time only given for spectra which we have used for line measurements rather than just redshift.
\end{tablenotes}
\end{threeparttable}
\end{center}
\label{tab:obs}
\end{table*}
\begin{figure*}
\includegraphics[width=\textwidth]{figs/gal_spec.png}
\caption{The spectrum of DES16C2ggt, decomposed into its constituent components according to the \texttt{pPXF} fit. 
\label{fig:host_spec}}
\end{figure*}

@@

In order to subtract the stellar component of the host galaxy spectra, we use the Penalized PiXel-Fitting software (\texttt{pPXF}; \citealt{Cappellari2004,Cappellari2012,Cappellari2017}), using the MILES library of single stellar populations \citep{Vazdekis2010}. By subtracting the best-fitting composite stellar spectrum from the \texttt{pPXF} fit, we are left with a `gas' spectrum, comprising the emission lines. An example of this procedure is shown in Fig. \ref{fig:host_spec}. We fit the emission lines using \texttt{PySpecKit} \citep{Ginsburg2011}. In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding a perturbation to the amplitude of the line by drawing from a Gaussian distribution centered on 0, and with a standard deviation equal to the root-mean-square (RMS) of the measured flux noise in a $100 \AA$ window around the central wavelength of the line. We take the mean and standard deviation of the resulting fits as our flux and its uncertainty, respectively.

@@

\section{Analysis and Discussion}
\label{sec:analysis} % used for referring to this section from elsewhere

\subsection{Stellar Mass \label{subsec:res_mass}}

@@

As for SFR, we show the cumulative distribution of sSFR in Fig.~\ref{fig:ssfr_cum}. The RET hosts are clearly shifted to higher sSFRs than CCSNe. To compare statistically the host sSFR distribution of RETs with the other samples, we employ the method of \citet{Wiseman2020}. For each pair of samples, we model the PDFs as skewed normal distributions. For both samples, we use identical normal priors for the `mean' and `scale'\footnote{See \citet{Wiseman2020} for a detailed description of the parameters describing the skewed normal distributions}, centred on the mean and twice the standard deviation of the two samples combined.

@@

\subsection{Comparison with AT2018cow \label{subsec:disc_cow}}
\phil{To add!}

>>>>

\toprule
{} &       RA &       Dec &    $m_r$\tnote{a}  &     $z$ &     Survey & Exposure time (hours) \tnote{b} \\
Transient name &          &           &          &         &         &            &               \\
\midrule
DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.6479 &      OzDES &       6.58 \\
DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.1964 &      OzDES &      10.16 \\
DES13S2wxf     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.5698 &      OzDES &       5.41 \\
DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.5823 &      OzDES &       4.00 \\
DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.7120 &      OzDES &      45.50 \\
DES13X3gmd     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.7808 &      OzDES &      13.91 \\
DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.3457 &  NOAO\_0522 &               \\
DES13C3uig     & 52.94416 & -27.58544 & $22.17 \pm 0.03$ & 0.6734 &       ACES &               \\
DES13X2wvv     & 34.86526 &  -6.71603 & $21.89 \pm 0.02$ & 0.4750 &      OzDES &       4.50 \\
DES14S2anq     & 41.27776 &  -0.74529 & $17.57 \pm 0.03$ & 0.0521 &      OzDES &       0.75 \\
DES14X1bnh     & 33.74902 &  -4.79254 & $21.95 \pm 0.03$ & 0.8298 &      OzDES &       3.50 \\
DES15S1fli     & 43.18790 &  -0.88620 & $20.98 \pm 0.02$ & 0.4473 &      OzDES &       2.33 \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citet{Wiseman2020}, not corrected for Galactic foreground reddening.
\item[b] Exposure time only given for spectra which we have used for line measurements rather than just redshift.
\end{tablenotes}
\end{threeparttable}
\end{center}
\label{tab:obs}
\end{table*}
\begin{figure*}
\includegraphics[width=\textwidth]{figs/gal_spec.png}
\caption{The spectrum of DES16C2ggt, decomposed into its constituent components according to the \texttt{pPXF} fit. 
\label{fig:host_spec}}
\end{figure*}

@@

In order to subtract the stellar component of the host galaxy spectra, we use the Penalized PiXel-Fitting software (\texttt{pPXF}; \citealt{Cappellari2004,Cappellari2012,Cappellari2017}), using the MILES library of single stellar populations \citep{Vazdekis2010}. By subtracting the best-fitting composite stellar spectrum from the \texttt{pPXF} fit, we are left with a `gas' spectrum, comprising the emission lines. An example of this procedure is shown in Fig. \ref{fig:host_spec}. We fit the emission lines using \texttt{PySpecKit} \citep{Ginsburg2011}. In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding perturbations to the line by drawing from a Gaussian distribution centered on 0, and with a standard deviation equal to the root-mean-square (RMS) of the measured flux noise in a 100~\AA~window around the central wavelength of the line. We take the mean and standard deviation of the resulting fits as our flux and its uncertainty, respectively.

@@

\section{Analysis}
\label{sec:analysis} % used for referring to this section from elsewhere

@@

As for SFR, we show the cumulative distribution of sSFR in Fig.~\ref{fig:ssfr_cum}. The RET hosts are clearly shifted to higher sSFRs than CCSNe. To statistically compare the host sSFR distribution of RETs with the other samples, we employ the method of \citet{Wiseman2020}. For each pair of samples, we model the PDFs as skewed normal distributions. For both samples, we use identical normal priors for the `mean' and `scale'\footnote{See \citet{Wiseman2020} for a detailed description of the parameters describing the skewed normal distributions}, centred on the mean and twice the standard deviation of the two samples combined.

@@

\subsection{Comparison with AT2018cow \label{subsec:disc_cow}}

The nearby transient AT2018cow has drawn many comparisons to the cosmological RETs from DES and PS1 \citep[e.g.][]{Perley2019,Margutti2019,Mohan2020,Fox2020} due to its rapid evolution and blue colour.
